On Secure Delegation of SampBQP with a Classical Client

### 2020-03-15 qpip.tex
Start rewriting SampBQP part

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
\Ethan{Properly intro and point out the difference between BQP and SampBQP and the challenge here.}
In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not work in our case, so we give the following construction instead.

First, we make an observation.

@@

@@

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	\begin{itemize}
		\item Let $\varepsilon>0$
		\item Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item Let $n$ be large enough so both
			$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$$
			and
			$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$$ are negligible in $\varepsilon$ by Chernoff bound
		\item Let $N$ be large enough so that $$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
			where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
	\end{itemize}
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item Set counter $c=0$
		\item Set $y=\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \cref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}

>>>>

In this section, we construct a $\QPIP_1$ delegation protocol for $\SampBQP$.
The high level idea is cut-and-choose; that is,
the server constructs multiple copies of the ground state as certificates,
the client then randomly chooses a copy to output and checks the rest.
There are two main challenges to this approach.
First, the client needs to reliably extract the circuit's output from its corresponding ground state,
which can be accomplished by padding the circuit with identity gates at the end.
Then, the clock register measures into after the last gate with high probability,
which implies that the data register is in the circuit's final state.
The other challenge is that a cheating prover could create arbitrary entanglements between its certificates.
This challenge isn't present in the protocol for $\BQP$ because its soundness is one-sided.
That is, we allow a cheating server to cause the client to reject a yes-instance;
it just can't convince the client to accept a no-instance.
Because of this asymmetry, it turns out that any prover, honest or not, can't do better than sending $n$ identical copies of some state,
which allows the use of Chernoff bound.
Here we use de Finetti's theorem to approximate our measurement results with unentangled states,
which comes with a cost of inverse polynomial errors,
to also allow the use of Chernoff bounds.

@@

\def\Samp{\mathsf{Samp}}
\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
\nc{\VSamp}{\ensuremath{V_\Samp}}
\nc{\PSamp}{\ensuremath{P_\Samp}}
\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}

\def\GS{\mathsf{GS}}

@@

\begin{protocol}{$\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ with soundness error $O(\varepsilon)$}
	\label{ProtoQPIP1}
	Let $C'$ be $C$ padding with enough identity gates so that...
	Let $n$ be large enough so by Chernoff bound
		$$P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
		$$P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]<\varepsilon$$
	Let $N$ be large enough so that by de Finetti's theorem...
		That is,
		$$\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$$
		where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$
	\begin{enumerate}
		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$
		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$. It then privately samples $k\in[N]\setminus I$.
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item The prover sends the $i$-th copy of $\ket{\psi_{C'(x)}}$, $\rho_i$, qubit-by-qubit.
			\item If $i\in I$, the verifier runs $\cA_{\GS}$ on $\rho_i$. Otherwise, if $i=k$, the verifier measures the data register of $\rho_i$ and save the outcome as $y$. Otherwise the verifier discards $\rho_i$.
		\end{enumerate}
		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the client accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}
